\documentclass[11pt,a4paper,sans]{moderncv} 
\usepackage{multicol}
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}



\newcommand{\MYhref}[3][gray]{\href{#2}{\color{#1}{#3}}}%


\moderncvstyle{casual} 
\moderncvcolor{blue} 

\usepackage[scale=0.75]{geometry}

\name{Mateusz}{Hazy}
\title{Curriculum Vitae} 
\address{Torfowa 14}{51-170 Wrocław}{Poland} 
\phone[mobile]{+48~782~770~550} 
\email{mateuszhazy@gmail.com}
\social[github]{matiwertyl2}

\begin{document}
\makecvtitle

\section{Education}
\cventry{2016--2019}{Bachelor of Science}{
\MYhref{http://www.ii.uni.wroc.pl/}{University of Wrocław}}{}{}{Joint Studies in Computer Science and Mathematics. Currently enrolled.}
\cventry{2013--2016}{High School Diploma}{
\MYhref{http://lo14.wroc.pl/}{14th High School}}{Wrocław}{}{Individualized course of study and participant of the science camps in Informatics and Mathematics.
Graduated receiving headmaster award for science achievements.} 

\section{Experience}
\cventry{2018}{Software Developer Intern}{}{\MYhref{https://www.gresearch.co.uk/}{G-Research}, London}{}{Created service for uploading and browsing multi-file documents. Server was written in ASP.NET Core and deployed on Kubernetes. User interface was made in Angular 6.} 
\cventry{2017}{Software Developer Intern}{}{\MYhref{https://www.samsung.com/pl/aboutsamsung/careers/careers-center/}{Samsung R\&D Institute Poland}, Warsaw}{}{Involved in HbbTV maintenance project. Used technologies: C++, Python, Bash.}
\cventry{2016--2017}{Tutor and Teacher}{\MYhref{http://www.ii.uni.wroc.pl/}{University of Wrocław}}{}{}{Teached algorithms during science camps, prepared students for the Polish
Olympiad in Informatics and organised programming \MYhref{http://solve.edu.pl/~sparingi/}{workshops}.}


\section{Languages}
\hspace*{\dimexpr\hintscolumnwidth+\separatorcolumnwidth\relax}
\begin{minipage}{\maincolumnwidth}
\begin{multicols*}{3}
\item \textbf{English} Fluent 
\item \textbf{German} Basic
\item \textbf{Polish} Native
\end{multicols*}
\end{minipage}



\section{Computer skills}
\cvitem{Programming}{C++, C\#, Java, JavaScript, Python}
\cvitem{}{Algorithms and data structures, Machine learning}
\cvitem{Web}{HTML, Angular}
\cvitem{Other}{Bash, Linux user, Git}{}{}

\section{Awards}
\cvitemwithcomment{}{Bronze Medal in the 23rd Polish Olympiad in Informatics}{\MYhref{http://www.oi.edu.pl/contestants/Mateusz\%20Hazy/}{}}
\cvitemwithcomment{}{Bronze Medal in the 7th Open team Programming Contest in Opole}{
\MYhref{https://wu.po.opole.pl/najlepiej-programuja-pedzace-zolwie/}{}}
\cvitemwithcomment{}{Wrocław Government Scholarship holder in 2015/2016 and 2016/2017}{}

\section{Interests}
\cvitem{}{Ice hockey, gym, travelling, fantasy books}


\end{document}